Treating Similarity with Respect: How to Evaluate Models of Meaning?

### 2016-05-14 paper.tex
Sync
Getting ready for the final version

% \aclfinalcopy % Uncomment this line for the final submission
\def\aclpaperid{19} %  Enter the acl Paper ID here

@@

% \author{First Author \\
%   Affiliation / Address line 1 \\
%   Affiliation / Address line 2 \\
%   Affiliation / Address line 3 \\
%   {\tt email@domain} \\\And
%   Second Author \\
%   Affiliation / Address line 1 \\
%   Affiliation / Address line 2 \\
%   Affiliation / Address line 3 \\
%   {\tt email@domain} \\}

@@

\newcite{Steels2010a} introduces the idea of language sub-systems and language strategies. A language subsystem is a means of expressing certain related or similar meanings. Examples of such sub-systems include:
\begin{compactitem}
    \item Lexical systems which express colours.
    \item Morphological devices to encode tenses.
    \item Using word order to express relations between agent and patient.
\end{compactitem}  
The later is an illustration of a language strategy. In English agent-patient relations are mainly encoded by syntax whereas German would use intonation and a combination or articles and case to convey the same information. Russian in contrast will use morphological devices for the same purpose.

>>>>

\aclfinalcopy % Uncomment this line for the final submission
\def\aclpaperid{19} %  Enter the acl Paper ID here

@@

\author{Dmitrijs Milajevs \\
  Queen Mary University of London \\
  London, UK \\
  {\tt d.milajevs@qmul.ac.uk} \\\And
  Sascha Griffiths \\
  Queen Mary University of London \\
  London, UK \\
  {\tt s.griffiths@qmul.ac.uk} \\
}

@@

\newcite{Steels2010a} introduces the idea of language sub-systems and language strategies. A language subsystem is a means of expressing certain related or similar meanings. Examples of such sub-systems include:
\begin{compactitem}
    \item Lexical systems which express colours.
    \item Morphological devices to encode tenses.
    \item Usage of word order to express relations between agent and patient.
\end{compactitem}  
The later is an illustration of a language strategy. In English agent-patient relations are mainly encoded by syntax whereas German would use intonation and a combination or articles and case to convey the same information. Russian in contrast will use morphological devices for the same purpose.
